Supplement Materials of Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-05-02 products/manuscript/supplement/Supplementary-Material.qmd
update project

---
title: "Supplement Materials of Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

This shows some materials that could go into a supplementary file. Often you want/need references here too. You can use the same reference bib file for this and the main text (as done here) or have separate bib files.

For illustrative purposes, I'm doing the supplement as pdf. For this to work, you need a (La)TeX system installed. It's easy. Just follow [these steps](https://quarto.org/docs/output-formats/pdf-basics.html).

Of course you would choose the format based on needs.

I'm also using a different style for the references here. (vancouver vs apa in the main manuscript). Usually one would have the formatting of the references the same in those two documents, but I want to illustrate how easy it is to switch reference formatting styles, you just need to get the right CSL file and specify it in the YAML header. We could also have a seperate reference bibtext (`.bib`) file, but here we are using the same.

@@

```{r}
# Load necessary package for ROC analysis
library(pROC)

# Generate predicted probabilities using the logistic regression model (model_gravidity)
promo_data_young$predicted_prob <- predict(model_gravidity, type = "response")

# Create the ROC curve
roc_obj <- roc(promo_data_young$adverse_birth_outcome, promo_data_young$predicted_prob)
plot(roc_obj, col = "blue", lwd = 2, main = "ROC Curve for Model: Gravidity in Women < 25")
auc_value <- auc(roc_obj)
print(paste("AUC:", round(auc_value, 2)))

# Load necessary package for calibration plot
library(caret)

# Create a calibration plot
calibration_data <- data.frame(
  observed = factor(promo_data_young$adverse_birth_outcome, levels = c(0,1)),
  predicted = promo_data_young$predicted_prob
)

# Use the calibration function from the caret package
cal_plot <- calibration(observed ~ predicted, data = calibration_data, class = "1")
plot(cal_plot, main = "Calibration Plot for Model: Gravidity in Women < 25")

@@

# Heatmap of cross-validated AUC\nfor Elastic-net hyperparameter grid
```{r}
library(ggplot2)

enet_tune %>% 
  collect_metrics() %>% 
  filter(.metric=="roc_auc") %>% 
  ggplot(aes(x = log10(penalty), y = mixture, fill = mean)) +
    geom_tile() +
    scale_fill_viridis_c(name = "AUC") +
    labs(
      x = expression(log[10](lambda)),
      y = expression(alpha),
      title = "Heatmap of cross-validated AUC\nfor Elastic-net hyperparameter grid"
    ) +
    theme_minimal(base_size = 12)

```{r}

>>>>

---
title: "Supplement Materials of Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
resources:
  - Images/**
execute:
  root: products/manuscript
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r roc-calibration, echo=TRUE, message=FALSE, warning=FALSE}
# 1) Load required libraries
library(dplyr)
library(pROC)
library(caret)
library(here)

# 2) Read cleaned data and subset to women < 25
promo_data_clean <- read.csv(here("data/clean/PROMO_Data_clean.csv"))
promo_data_young <- promo_data_clean %>%
  filter(age_at_enrollment_years < 25) %>%
  mutate(
    # Composite adverse outcome: 1 if preterm, stillbirth, or low birth weight
    low_birth_weight      = as.integer(birth_weight < 2.5),
    adverse_birth_outcome = as.integer(
      preterm_births_count > 0 |
      stillbirth_bin == 1        |
      low_birth_weight == 1
    )
  )

# 3) Fit logistic regression model
model_gravidity <- glm(
  adverse_birth_outcome ~ gravidity + total_malaria_episodes +
    study_arm + education_level,
  family = binomial(link = "logit"),
  data   = promo_data_young
)

# 4) Generate predicted probabilities
promo_data_young$predicted_prob <- predict(
  model_gravidity,
  newdata = promo_data_young,
  type    = "response"
)

# 5) ROC curve and AUC
roc_obj  <- roc(
  promo_data_young$adverse_birth_outcome,
  promo_data_young$predicted_prob
)
plot(
  roc_obj,
  col   = "blue",
  lwd   = 2,
  main  = "ROC Curve: Gravidity Model (Age < 25)"
)
auc_val <- auc(roc_obj)
cat("AUC:", round(auc_val, 2), "\n")

# 6) Calibration plot
data_cal <- data.frame(
  observed = factor(promo_data_young$adverse_birth_outcome, levels = c(0,1)),
  predicted = promo_data_young$predicted_prob
)
cal_plot <- calibration(
  observed ~ predicted,
  data  = data_cal,
  class = "1"
)
plot(cal_plot, main = "Calibration Plot: Gravidity Model (Age < 25)")

@@
